archive_methods

### 2020-03-21 non_publication/manuscript/original_bookdown_files/03-methods.Rmd
moved to non_publication folder (iii)
Files that are not being used in the final manuscript were moved into a non_publication folder as a holding step. Next step is dependent on each file, either delete, keep here or consolidate further.

# Methods
### Study site
Research was conducted at the 25.6 ha ForestGEO (Global Earth Observatory) study plot at the Smithsonian Conservation Biology Institute (SCBI) in Virginia, USA (38°53'36.6"N, 78° 08'43.4"W) [@andersonteixeira_ctfs-forestgeo:_2015]. SCBI is located in the central Appalachian Mountains at the northern edge of Shenandoah National Park.  Elevations range from 273-338m above sea level [@gonzalezakre_patterns_2016] with a topographic relief of 65m [@bourg_initial_2013]. Dominant species include *Liriodendron tulipifera*,  oaks (*Quercus* spp.), and hickories (*Carya* spp.).

@@

species <- read.csv(text=getURL("https://raw.githubusercontent.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/master/data/core_list_for_neil.csv?token=AJNRBEIAVYFAN2CJB3Y3UAS5D5BNG"), stringsAsFactors = FALSE)

@@

traits_table <- data.frame(
  "Trait" = c("Ring Porosity", "Percent Leaf Area", "Leaf Mass Area", "Chlorophyll", "Wood density", "TLP", "P50", "P80"),
  "Unit" = c("ring, semi-ring, diffuse", "%", "g/m2", "m2/g", "g/cm3", "MPa", "MPa", "MPa"))
traits_table$abb <- c("rp", "PLA", "LMA", "Chl", "WD", "TLP", "p50", "p80")

@@

for (i in seq(along=traits_table$abb[2:8])){
  trait <- traits_table$abb[2:8][i]

  sub <- trees_all[grepl(trait, colnames(trees_all))]
  traits_table$mean[2:8][i] <- ifelse(grepl(trait, colnames(sub)), 
                              mean(sub[, 1], na.rm=TRUE), 
                              traits_table$mean)

  traits_table$min[2:8][i] <- ifelse(grepl(trait, colnames(sub)), 
                              min(sub[, 1], na.rm=TRUE), 
                              traits_table$min)

  traits_table$max[2:8][i] <- ifelse(grepl(trait, colnames(sub)), 
                              max(sub[, 1], na.rm=TRUE), 
                              traits_table$max)
}

@@

kable(traits_table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

@@

```{r, all_candidates, eval=TRUE, echo=TRUE, message=FALSE}
candidates <- read.csv("tables_figures/candidate_traits.csv")
kable(candidates) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

>>>>

```{r include=FALSE, cache=FALSE}
rm(list = ls(all = TRUE))
```
# Methods
### Study site
Research was conducted at the 25.6 ha ForestGEO (Global Earth Observatory) study plot at the Smithsonian Conservation Biology Institute (SCBI) in Virginia, USA (38°53'36.6"N, 78° 08'43.4"W) [@andersonteixeira_ctfs-forestgeo:_2015]. SCBI is located in the central Appalachian Mountains at the northern edge of Shenandoah National Park.  Elevations range from 273-338m above sea level [@gonzalezakre_patterns_2016] with a topographic relief of 65m [@bourg_initial_2013]. Dominant species include *Liriodendron tulipifera*,  oaks (*Quercus* spp.), and hickories (*Carya* spp.).

@@

species <- read.csv("D:/Dropbox (Smithsonian)/Github_Ian/McGregor_climate-sensitivity-variation/data/core_list_for_neil.csv", stringsAsFactors = FALSE)

@@

traits_table <- data.frame(
  "Trait" = c("Ring Porosity", "Percent Leaf Area", "Leaf Mass Area", "Wood density", "TLP"),
  "Unit" = c("ring, semi-ring, diffuse", "%", "g/m2", "g/cm3", "MPa"))
traits_table$abb <- c("rp", "PLA", "LMA", "WD", "TLP")

@@

for (i in seq(along=traits_table$abb[2:5])){
  trait <- traits_table$abb[2:5][i]

  sub <- trees_all[grepl(trait, colnames(trees_all))]
  traits_table$mean[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              mean(sub[, 1], na.rm=TRUE), 
                              traits_table$mean)

  traits_table$min[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              min(sub[, 1], na.rm=TRUE), 
                              traits_table$min)

  traits_table$max[2:5][i] <- ifelse(grepl(trait, colnames(sub)), 
                              max(sub[, 1], na.rm=TRUE), 
                              traits_table$max)
}

@@

kable(traits_table) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

```{r, all_candidates, eval=TRUE, echo=FALSE, message=FALSE}
candidates <- read.csv("tables_figures/candidate_traits.csv")
kable(candidates) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

### 2020-03-21 non_publication/manuscript/original_bookdown_files/05-discussion.Rmd
moved to non_publication folder (iii)
Files that are not being used in the final manuscript were moved into a non_publication folder as a holding step. Next step is dependent on each file, either delete, keep here or consolidate further.

#### misc content to integrate
From [@kannenberg_linking_2019], species with diffuse porous wood anatomy (*Liriodendron*) are more sensitive to drought, whereas ring-porous are not as affected because they more easily rebuild structures for hydraulic conductivity. This paper mentions it would be good to have this data with respect to latent affects from drought.

>>>>

### misc content to integrate
From [@kannenberg_linking_2019], species with diffuse porous wood anatomy (*Liriodendron*) are more sensitive to drought, whereas ring-porous are not as affected because they more easily rebuild structures for hydraulic conductivity. This paper mentions it would be good to have this data with respect to latent affects from drought.
